---
title: "Getting Started with Binomial"
author: "Zishen Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


## Binomial Distribution

The package `"binomial"` is an implementation to find various properties and probabilities of the binomial distribution. It also provides the option of visualizing the distribution and listing out the summary statistics.


## Basic Binomial Related Functions

The package provides many ready to use functions including `"bin_choose(n, k)"`, `"bin_probability(sucess, trials, prob)"`, `"bin_mean(trials, prob)"`, `"bin_variance(trials, prob)"`, `"bin_mode(trials, prob)"`, `"bin_skewness(trials, prob)"`, `"bin_kurtosis(trials, prob)"`. Some of these are shown as examples:

```{r}
bin_choose(5, 3)
bin_probability(1:3, 5, 0.2)
bin_mean(10, 0.3)
```

For invalid values, the functions will output an error.



## Creating Binomial Distributions

The package allows the user to create binomial distributions and binomial cumulative distributions. For each, there is the option of visualizing the distribution:

```{r}
dis1 <- bin_distribution(trials = 10, prob = 0.5)
plot(dis1)
dis2 <- bin_cumulative(trials = 10, prob = 0.5)
plot(dis2)
```

## Summary Statistics

You can create a `"binvar"` object to get summary statistics of a particular binomial distribution:

```{r}
bin1 <- bin_variable(5, 0.4)
bin1
```

```{r}
binsum1 <- summary(bin1)
binsum1
```

