---
title: "Getting Started with Binomial"
author: "Zishen Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


## Binomial Distribution

The package `"binomial"` is an implementation to find different properties and probabilities of the binomial distribution. It also provides the option of visualizing the distribution and listing out the summary statistics.

One major formual that we used is the following:

$$Pr(X = k) = \binom{n}{k}p^k(1-p)^{n-k}$$

* *n* is the number of fixed trials ($n \geq 0$)
* *p* is the probability of success on each trial ($0 \leq p \leq 1$)
* *1-p* is the probability of failure on each trial 
* *k* is the number of successes out of n trials ($0 \leq k \leq n$)
* $\binom{n}{k}$ is the number of combinations in which *k* successes can occur in *n* trials

## Basic Binomial Related Functions

The package provides many ready to use functions including `"bin_choose(n, k)"`, `"bin_probability(sucess, trials, prob)"`, `"bin_mean(trials, prob)"`, `"bin_variance(trials, prob)"`, `"bin_mode(trials, prob)"`, `"bin_skewness(trials, prob)"`, `"bin_kurtosis(trials, prob)"`. 

* `bin_choose()` finds the number of ways to choose k items from n 
* `bin_probability()` finds the probability of a particular number of successes 
* `bin_distribution()` creates a `"bindis"` and `"data.frame"` object that can be visualized with `plot()`
* `bin_cumulative()`creates a `"bincum"` and  `"data.frame"` object that can be visualized with `plot()`
* `bin_variable()` creates a `"binvar"` object that can be summarized with `summary()`
* `bin_mean()` finds the mean
* `bin_variance()` finds the variance
* `bin_mode()` finds the mode
* `bin_skewness()` finds the skewness
* `bin_kurtosis()` finds the kurtosis

Some of these are shown as examples:

```{r}
bin_choose(5, 3)
bin_probability(1:3, 5, 0.2)
bin_mean(10, 0.3)
```

For invalid values, the functions will output an error.



## Creating Binomial Distributions

The package allows the user to create binomial distributions and binomial cumulative distributions. For each, there is the option of visualizing the distribution:

```{r}
dis1 <- bin_distribution(trials = 10, prob = 0.5)
plot(dis1)
dis2 <- bin_cumulative(trials = 10, prob = 0.5)
plot(dis2)
```

## Summary Statistics

You can also get summary statistics of a particular binomial distribution:

```{r}
bin1 <- bin_variable(5, 0.4)
bin1
```

```{r}
binsum1 <- summary(bin1)
binsum1
```

